Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-09 Paper/paper.tex
Template files fleshing out

\subsection{Template Files}
In order to get developers up and running as quickly as possible, we've included a couple template files below that will get them started out.

The first file is the \lstinline{package.json} file that includes the dependencies for the unit testing, UI testing, and grunt portions of the workflow:
\begin{lstlisting}
{
  "name": "MODULE_NAME", // Edit Me
  "version": "SOME_NUMBER", // Edit Me
  "dependencies": {
    "grunt": "latest",
    "grunt-contrib-watch": "latest",
    "grunt-shell": "latest",
    "grunt-mocha-test": "^0.10.2"
    "mocha": "^1.18.2",
    "istanbul": "^0.2.7",
    "nightwatch": "^0.4.9",
    "chai": "^1.9.1"
  }
}
\end{lstlisting}

@@

    // Register the code coverage task
    grunt.registerTask('test_with_coverage', ['shell:istanbul', 'watch:coverage']);
};
\end{lstlisting}

>>>>

\subsection{Template Files}
In order to get developers up and running as quickly as possible, we've included a couple template files below.

The first file is the \lstinline{package.json} file that includes the dependencies for the unit testing, UI testing, and grunt portions of the workflow:
\begin{lstlisting}
{
  "name": "MODULE_NAME", // Edit Me
  "version": "SOME_NUMBER", // Edit Me
  "dependencies": {
    "grunt": "latest",
    "grunt-contrib-watch": "latest",
    "grunt-shell": "latest",
    "grunt-mocha-test": "^0.10.2"
    "mocha": "^1.18.2",
    "istanbul": "^0.2.7",
    "nightwatch": "^0.4.9",
    "chai": "^1.9.1"
  }
}
\end{lstlisting}
The developer should put this file in the main folder of their project, the folder where they will run commands from. It is not necessary for the folder to be the same folder that the tests are in, just a central location where the developer expects the most work to be done. This file can be copied into other directories if the developer expects to run the testing and grunt commands from multiple directories.

@@

    // Register the code coverage task
    grunt.registerTask('test_with_coverage', ['shell:istanbul', 'watch:coverage']);
};
\end{lstlisting}
The developer will want to put the Gruntfile in the same folder as the \lstinline{package.json} file. This template file comes with a \lstinline{default} task, an \lstinline{update} task, a \lstinline{test} task, and a \lstinline{test_with_coverage}. The \lstinline{default} will run the Mocha tests one time, with no additional watch functionality. The \lstlisting{update} task that will update the dependencies. We recommend that the developer run the \lstinline{update} task at least once a day to keep dependencies and executables up to date. The \lstinline{test} task will run the Mocha tests with watch functionality so that the tests will run on every save of the source files. The \lstinline{test_with_coverage} task will run the Mocha tests with \emph{coverage} in addition to the watch functionality.

With these two files, the developer will have a testing workflow set up with minimal effort.
